---
title: "Covid-19 in Belgium"
author: "Huy Nguyen"
date: "31/07/2021"
output: slidy_presentation
urlcolor: blue
linkcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Introduction


In March 2019, Covid-19 reached Belgium, starting in one province and spread out over the whole country in few months.

We have developed a small web application that shows the number of Covid-19 hospitalisations by provinces during the period of 2020-03-15 to 2021-07-27.

The data are provided by Sciensano, the Belgian institute for health, and are available at <https://epistat.wiv-isp.be/covid/> under the section “Datasets/Hospitalisations by date and provinces”.

The web application is hosted at  
&nbsp;&nbsp;&nbsp;&nbsp;  <https://huy-s-nguyen.shinyapps.io/Covid-19-in-Belgium-2021/>
  
The code of the web application, ui.R and server.R, can be found at  
&nbsp;&nbsp;&nbsp;&nbsp;  <https://github.com/huy-seraphim-nguyen/Shiny-Application/>    
  

## The application

The application can be ran online by visiting the URL  
&nbsp;&nbsp;&nbsp;&nbsp;  <https://huy-s-nguyen.shinyapps.io/Covid-19-in-Belgium-2021/>

The application presents 2 panels:<br>
 
- The left panel provides the selection of a province, using a drop down list menu.
- The right panel presents a barplot of the Total number of hospitalisations by provinces.<br>
It also shows the number of hospitalisations of the province you selected in the left panel.
 
## Example application output (right panel)
<br>
An example of the right panel when user selects "Brussels" as province.
<br>
<br>

```{r , echo = FALSE, warning=FALSE, results = "asis"}
library(ggplot2)
# Global data & variables
df <- read.csv("COVID19BE_HOSP.csv")
df <- df[, c("PROVINCE", "TOTAL_IN")]

# aggregate data by PROVINCE
df1 <- aggregate(. ~ PROVINCE, data = df, FUN = sum)

# replace the French(accent) name
df1[5,1]<-"Liege"


p <- ggplot(data=df1, aes(x=PROVINCE, y=TOTAL_IN)) +
          geom_bar(stat="identity", fill="steelblue") + coord_flip()
print(p)

# write new line
writeLines("\n")
 
res <- df1[df1$PROVINCE=="Brussels",]
msg <- paste("Total hospitalisations in ", res[1], " : ", res[2] )

# print msg without surrounding quotes and leading []
cat(msg)
```

## Thank you for your attention
 
 
 

